Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-18 paper/paper.tex
Add additional information to introduction and finalize analyse subsection

Therefore, there is a need in the community to find the answer to what makes for a high quality, valuable software ticket 
that would improve the overall performance of the development team and, inherently, the company. As there are many 
fields in a ticket, the number of unanswered questions is rather large: do stack traces have an influence on the quality
of a ticket? What about attachments and whether a screenshot is more helpful than a snippet of code? Does a negative sentiment
drawn from comments increase or decrease the time taken to solve a bug? How does grammar correctness influence the 
communication friction?

@@

During the analysis part, we investigate several variables in correlation with \emph{time-to-complete}, 
which we define as the \emph{metric of quality} (\emph{time-to-complete} represents the period of time between the creation 
and the closing of a ticket). There are multiple novel aspects brought by our study, among which is the fact that it is one of 
the very few studies that have tackled this issue using a quantitative rather than a qualitative approach (with a very 
large number of tickets analysed) and also that it uses state-of-the-art sentiment \cite{wilson2005recognizing} as well as 
grammar correctness analysis techniques \cite{wilson2005recognizing}. We believe that our results are valuable 
contributions to the research community and the database produced after the analysis can help further studies with 
analyzed and well-tested data.

\section{Related Work}

\section{Building the Data Set}
The first step towards building the data set was to create a tool that was able to execute all the commands that we required:
fetching the tickets from any Jira instance, storing them into some form of database, analyze the variables of interest, 
automatically plot the correlations between them and run statistical analysis on the data. After careful consideration, 
we decided that Go was the best way to go for various reasons:
  \begin{itemize}
    \item it is designed with simplicity in min, thus making it easier for others who might join the project to read 
    and understand the codebase;
    \item it is compiled, statically typed, which implies that it is a much faster candidate than other interpreted languages
    such as Ruby or Python;
    \item is is designed with concurrency in mind, thus it helps reduce times of execution and computing power considerably;
  \end{itemize}

@@

Implementation wise, the application first checks Bolt for tickets and gets either all of them in memory (easier to parse, 
but heavy on resource utilization) or slices them into smaller arrays to get processed afterwards (harder to parse as it 
eventually requires re-creation of the whole array of tickets before inserting back into the database, but it is much 
lighter on computing power). After having the tickets available, we start looping through them and perform all 
analysis types mentioned above. Once some sort of value is computed (e.g. grammar correctness score), it gets set in 
its corresponding field in the ticket struct and subsequently stored back in the database. We chose this approach because 
we do not want to run the analysis every time we want to plot correlations between variables, but rather have the data 
already available there. Moreover, for external analysis such as hitting Google Cloud Platform APIs, there are costs for 
running the analysis, thus in this way we drastically reduce overall costs for the project.

@@

\section{Characterising the Data Set}

\section{Correlations}

@@

\section{Future Work}

\section{Conclusions}

>>>>

Therefore, there is a need in the community to find the answer to what makes for a high quality, valuable software ticket 
that would improve the overall performance of the development team and, inherently, the company. As there are many 
fields in a ticket, there are numerous unanswered questions: do stack traces have an influence on the quality
of a ticket? What about attachments and whether a screenshot is more helpful than a snippet of code? Does a negative sentiment
drawn from comments increase or decrease the time taken to solve a bug? How does grammar correctness influence the 
communication friction?

@@

During the analysis part, we investigate several variables in correlation with \emph{time-to-complete}, 
which we define as the \emph{metric of quality}. \emph{time-to-complete} represents the period of time between the creation 
and the closing of a ticket; more specifically, the creation of the ticket is marked when the status of the ticket is set to 
\emph{Open} and the closing of a ticket is considered when the ticket status is set to \emph{Closed} (or some similar status, 
such as \emph{Fixed}, \emph{Resolved}). \emph{Time-To-Complete} is our dependent variable, and as independent variables 
(i.e. variables controlled in order to test the effects on the dependent variable) we have set a number of ticket fields.

This study brings several contributions to the research community:
\begin{itemize}
  \item it is one of the very few research projects that investigates such a large number of tickets (over 300,000) spanning
  across a variety of projects (i.e. 21 projects);
  \item it is one of the few studies in the field that performs a quantitative analysis rather than a qualitative one;
  \item it is, to our knowledge, the first study to conduct sentiment and grammar correctness analyses on software tickets.
\end{itemize}

In Section \ref{related_work} we iterate over state-of-the art studies in the field and then continue with 
Section \ref{building} where we discuss how the ticket data set was collected and analysed. We continue with describing 
the data set (Section \ref{characterising}) where we provide insights into various aspects of the data (e.g. size of database,
number of tickets with attachments) and then discuss about correlations between the variables (Section \ref{correlations}).
Finally, we provide future research directions in Section \ref{future_work} and present our conclusions in Section \ref{conclusions}.

\section{Related Work}\label{related_work}

\section{Building the Data Set}\label{building}
The first step towards building the data set was to create a tool that was able to execute all the commands that we required:
fetching the tickets from any Jira instance, storing them into some form of database, analyze the variables of interest, 
automatically plot the correlations between them and run statistical analysis on the data. After careful consideration, 
we decided that Go was the best way to go for various reasons:
  \begin{itemize}
    \item it is designed with simplicity in min, thus making it easier for others who might join the project to read 
    and understand the codebase;
    \item it is compiled, statically typed, which implies that it is a much faster candidate than other interpreted languages
    such as Ruby or Python;
    \item is is designed with concurrency in mind, thus it helps reduce times of execution and computing power considerably;
  \end{itemize}

@@

Implementation wise, the application first checks Bolt for tickets and gets either all of them in memory (easier to parse, 
but heavy on resource utilization) or slices them into smaller arrays to get processed afterwards (harder to parse as it 
eventually requires re-creation of the whole array of tickets before inserting back into the database, but it is much 
lighter on computing power). After having the tickets available, we start looping through them and perform all 
analysis types mentioned above. Once some sort of value is computed (e.g. grammar correctness score), it gets set in 
its corresponding field in the ticket struct and subsequently is stored back in the database. We chose this approach because 
we do not want to run the analysis every time we want to plot correlations between variables, but rather have the data 
already available there. Moreover, for external analysis such as hitting Google Cloud Platform APIs, there are costs for 
running the analysis, thus in this way we drastically reduce overall costs for the project.

@@

Afterwards, we have created two extra commands for automatically generating plots (i.e. scatter plots and bar charts) and 
running statistical tests on the collected data.

For plotting the data, we first connect again to the Bolt database instance and then filter out only the issues that have 
the variable \emph{Time-To-Close} set (i.e. tickets marked as closed when they were fetched from the Jira instance). Afterwards,
we either save scatter plots or bar charts to disk.

Also, in order to validate our findings, the statistics command fetches all the data from the database and

\section{Characterising the Data Set}\label{characterising}

\section{Correlations}\label{correlations}

@@

\section{Future Work}\label{future_work}

\section{Conclusions}\label{conclusions}
